Source Summaries

### 2020-02-02 sourceSummaries.tex
Changed bibentry
Fixed error's in people's code, it now compiles correctly
Fixed overfull hbox issue

\documentclass[letterpaper,12pt]{article}
\usepackage{natbib}
\usepackage{bibentry}
\usepackage[hyphens]{url}
\usepackage[numbib]{tocbibind}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}

@@

\noindent
\section{Filizzola 2018 Security}
\subsection{Citation}

\noindent

@@

\noindent
\subsection{Citation}
\Urlmuskip=0mu plus 1mu\relax
\bibentry{8622000}

@@

\noindent
The authors detail the encryption and authentication standards found in the Bluetooth Low Energy Protocol, from Bluetooth 4.0 to Bluetooth 5.0.  The researchers also look at several BLE devices to analyze their security models.
\subsection{Theory}

@@

\section{Finding Vulnerabilities in IoT Devices: Ethical Hacking of Electronic Locks}

\noindent
\subsection{Citation}
\Urlmuskip=0mu plus 1mu\relax
\bibentry{8622000}

@@

\noindent
The authors outline how to approach attacking Bluetooth locks in a scientific fashion. They use well documented attacks and threat modeling to discover vulnerabilities in a Bluetooth low energy lock.
\subsection{Theory}

>>>>

\documentclass[letterpaper,12pt]{article}
\usepackage{natbib}
\usepackage{bibentry}
\usepackage[hyphens]{url}
\usepackage[numbib]{tocbibind}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\include{references.bib}

@@

\noindent
\section{Security Analysis of Bluetooth Technology}

\noindent
\subsection{Citation}

@@

\noindent
\subsection{Group member}
Joshua Niemann
\subsection{Citation}

\Urlmuskip=0mu plus 1mu\relax
\bibentry{8622000}

@@

\noindent
The authors detail the encryption and authentication standards found in the Bluetooth Low Energy Protocol, from Bluetooth 4.0 to Bluetooth 5.0.  The researchers also look at several BLE devices to analyze their security models.

\noindent
Game Theory is the primary theory being tested in this article.  The authors examine various versions of the Bluetooth protocol to determine which versions have the best security measures in place.  In addition, the authors analyze BLE devices in an effort to learn which devices and device manufacturers have the best security.

@@

\section[Finding Vulnerabilities in IoT Devices: Ethical Hacking of Electronic Locks]{Finding Vulnerabilities in IoT Devices: Ethical \\Hacking of Electronic Locks}

\noindent
\subsection{Citation}

\Urlmuskip=0mu plus 1mu\relax
\bibentry{KTH}

@@

\noindent
The authors outline how to approach attacking Bluetooth locks in a scientific fashion. They use well documented attacks and threat modeling to discover vulnerabilities in a Bluetooth low energy lock.
